### 2017-01-21 intro.tex
quad thm part3 completed

The asymptotic convergence of 1SPSA algorithm requires one extra assumption other than the conditions specified in the FDSA scheme above. The extra condition for convergence of $\theta_n$ to $\theta^*$  is as follows:
\item $\{\Delta_{ni}, i=1,\ldots,N, n=1,2,\ldots\}$ are i.i.d., independent of $\F_n$ and for some $\alpha_0 > 0$ and $\forall n$, $\E (\Delta_{ni})^{-2} \le \alpha_0$, for $i = 1,2,\ldots,N$.
Since 1SPSA randomly perturbs the parameter vector $\theta$, the number of function measurements required is two, irrespective of the dimension of $\theta$, see that the numerator of \eqref{eq:spsa} is the same in all $N$ components of $\widehat{\nabla} f(\theta_{n})$. However, inspite of the fact that the 1SPSA requires only two function measurements compared to  $2N$  measurements required by FDSA, the asymptotic convergence rate is the same as the FDSA scheme.

>>>>

The asymptotic convergence of 1SPSA algorithm requires one extra assumption other than the conditions specified in the FDSA scheme above. The extra condition for convergence of $\theta_n$ to $\theta^*$  is as follows:
\begin{pvn}
\item $\{\Delta_{ni}, i=1,\ldots,N, n=1,2,\ldots\}$ are i.i.d., independent of $\F_n$ and for some $\alpha_0 > 0$ and $\forall n$, $\E (\Delta_{ni})^{-2} \le \alpha_0$, for $i = 1,2,\ldots,N$.
\end{pvn}
Since 1SPSA randomly perturbs the parameter vector $\theta$, the number of function measurements required is two, irrespective of the dimension of $\theta$, see that the numerator of \eqref{eq:spsa} is the same in all $N$ components of $\widehat{\nabla} f(\theta_{n})$. The efficiency of 1SPSA depends on the shape of the objective function $f$, $\{a_n\}$, $\{\delta_n\}$ and the distribution of perturbation vectors, i.e., $\Delta_n$ $\forall n$. In \cite{spall}, in addition to establishing formal convergence of $\theta_n \to \theta^*$, it was shown that probability distribution of appropriately scaled $\theta_n$ is approximately normal  (with some mean and covariance matrix) for larger $n$. The general metric which is used for evaluating these class of algorithms is asymptotic mean squared error (AMSE) defined as $\E\l \theta_{n} - \theta^* \r^2$.  The relative efficiency of 1SPSA when compared to FDSA can be shown when we compare the similar asymptotic normality result of FDSA. In \cite{spall}, it was shown that under reasonably general conditions, and when $\{a_n\}$, $\{\delta_n\}$ are chosen according to the guidelines in \cite{spall1998implementation} then 1SPSA and FDSA gives same AMSE for given number of iterations. Instead of looking the 
\begin{align}\label{eq:amse}
\frac{\text{AMSE of 1SPSA}}{\text{AMSE of FDSA}}, 
\end{align}
an equivalent way of looking the relative AMSE is to compare the number of function measurements required by FDSA to achieve same AMSE as 1SPSA which can be computed by equating the \eqref{eq:amse} to one.
\begin{align}\label{eq:amsenom}
 \frac{\text{No.of function measurements for 1SPSA }}{\text{No.of function measurements for FDSA}}=  \frac{1}{N}.
\end{align}

%However, inspite of the fact that the 1SPSA requires only two function measurements compared to  $2N$  measurements required by FDSA, the asymptotic convergence rate is the same as the FDSA scheme.
